---
title: "Untitled"
output:
  word_document: default
  html_document: default
---

Importing data into the workspace and checking if there are any missing values in the data.
```{r}
data <- read.csv("~/Downloads/GERMAN_DATA.csv")
data[!complete.cases(data),]
```

Importing Myfunctions.R into the workspace

```{r}
setwd("/Users/ravalibongoni/Downloads")
source(("Myfunctions.R"))
```


```{r}
library(rpart)
library(rpart.plot)
```

Data Partitioning- 70% train data and 30% validation data
```{r}
set.seed(0)
p2 <- partition.2(data, 0.8)
data1.train <- p2$data.train
data1.val <- p2$data.val
```

Construct a classification tree on train data

```{r}
dt <- rpart(data1.train$Y ~ . , data = data1.train, method = "class",parms = list(loss = matrix(c(0, 5,1, 0), nrow = 2)))
```

Plot the constructed tree
```{r}
prp(dt, type = 1, extra = 1, under = TRUE, split.font = 2, varlen = -10)
```



get prediction on the validation data

```{r}
pred.val = predict(dt, data1.val, type = 'class')
conf(data1.val$Y, pred.val) 
```

Cost complexity pruning and printing the table
```{r}
cv.ct <- rpart(Y ~ . , data = data1.train, method = "class", cp = 0.00001, minsplit = 5, xval = 5,parms = list(loss = matrix(c(0, 5,1, 0), nrow = 2)))
printcp(cv.ct)
```

Prune the tree with minimum xerror
```{r}
prune.ct <- prune(cv.ct, cp = cv.ct$cptable[which.min(cv.ct$cptable[,"xerror"]), "CP"])
```

plot the pruned tree
```{r}
prp(prune.ct, type = 1, extra = 1, under = TRUE, split.font = 2, varlen = -10)
```

Evaluating performance of pruned tree
```{r}
pred.val = predict(prune.ct, data1.val, type = 'class')
conf(data1.val$Y, pred.val)
```
Performance is not good. looking for other cp value

prune the model with cp= 0.0173913

```{r}
prune.ct2 <- prune(cv.ct, cp = 0.0173913)
```

plot the pruned tree
```{r}
prp(prune.ct2, type = 1, extra = 1, under = TRUE, split.font = 2, varlen = -10)
```

Evaluating performance of pruned tree
```{r}
pred.val = predict(prune.ct2, data1.val, type = 'class')
conf(data1.val$Y, pred.val)
```
Better model with high sensitivity.














